Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/rec-intro.tex
Updated script
Revisions

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = \amb$ and $\recb = \bma$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any further command from $\reca$ or $\recb$ will break the filesystems.

@@

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}

@@

$\recb$ can be obtained in a similar way by reversing $A$ and $B$
in the definition.

\bigskip

\noindent
Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
let us introduce partial orders that describe under what conditions
sequences of commands work, that is, do not break a filesystem.

>>>>

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = \amb$ and $\recb = \bma$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any further command to $\reca$ or $\recb$ will break the filesystems.

@@

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
$\recb$ can be obtained in a similar way by reversing $A$ and $B$
in the definition.
\end{mydef}

@@

\myskip
Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
let us introduce partial orders that describe under what conditions
sequences of commands work, that is, do not break a filesystem.

### 2018-07-03 p2/works-inverse.tex
Revisions

\subsection{Domains of Sets}

\begin{mydef}[Sets of sequences]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
to denote such sets for brevity.

We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
\end{mydef}

@@

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.

Also, we write $\worksmnil{\sqs{A}}$ to mean that
there are filesystems on which all sequences in $\sqs{A}$ are defined.
If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.

@@

\begin{mylem}\mlabel{worksinputmatch}
If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
then the input types of these commands must match, i.e. $[x]=[z]$.
\end{mylem}
\begin{proof}
This result is similar to \cref{equiv_simple_same_commands} and
is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
either $\cxynv$ or $\czwnv$ would not break, 
and consequently $S$ and $T$ cannot work on the same filesystem.
\end{proof}

>>>>

\subsection{Domains of Sets of Command Sequences}

\begin{mydef}[Sets of sequences, their domains]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
to denote such sets for brevity.
We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
\end{mydef}

@@

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
Also, we write $\worksmnil{\sqs{A}}$ to mean that
there are filesystems on which all sequences in $\sqs{A}$ are defined.
If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.

@@

\begin{mylem}\mlabel{worksinputmatch}
If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
and there are commands $\cxynv\in S$ and $\czwnv\in T$ on the same node $n$,
then the input types of these commands must match, i.e. $[x]=[z]$.
\end{mylem}
\begin{proof}
This result is similar to \cref{equiv_simple_same_commands} and
is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
either $\cxynv$ or $\czwnv$ would not break, 
and consequently $S$ and $T$ cannot work on the same filesystem.
\end{proof}
